Self Regulation Ontology Retest Analyses

### 2018-06-06 code/SRO_Retest_Analyses.Rmd
adding post frisem analyses

Distributions of sum squared residual

```{r}
pred_sample_out %>%
  mutate(sq_diff_lit = (pred - retest_reliability)^2,
         sq_diff_emp = (pred - mean_icc)^2) %>%
  group_by(.n, task) %>%
  summarise(sum_sq_diff_lit = sum(sq_diff_lit),
            sum_sq_diff_emp = sum(sq_diff_emp)) %>%
  # select(-'.n') %>%
  gather(key, value, -task, -.n) %>%
  ggplot(aes(value, fill=key, color=task))+
  geom_density(size=1)+
  scale_fill_manual(breaks=c("sum_sq_diff_emp","sum_sq_diff_lit"),
                       labels=c("Empirical", "Literature"),
                      name="Predicting",
                      values = c("purple", "orange"))+
  scale_alpha_manual(breaks=c("survey", "task"),
                     values = c(0.4, 0.7),
                     name="Measure type")+
  scale_color_discrete(name="Measure type")
```

>>>>

Distributions of sum squared residual: Residuals are larger for tasks compared to surveys (i.e. predictions are worse when predicting task variables - possibly because their variability is higher?). For surveys the predictions of the literature are better than predictions of our data while the opposite is true for task measures.

Does this make sense with the results above? Figure out how to think of the noise ceiling analyses and LOOCV results together.

```{r}
pred_sample_out %>%
  mutate(sq_diff_lit = (pred - retest_reliability)^2,
         sq_diff_emp = (pred - mean_icc)^2) %>%
  group_by(.n, task) %>%
  summarise(sum_sq_diff_lit = sum(sq_diff_lit),
            sum_sq_diff_emp = sum(sq_diff_emp)) %>%
  # select(-'.n') %>%
  gather(key, value, -task, -.n) %>%
  ggplot(aes(value, fill=key, color=task, alpha=task))+
  geom_density(size=1)+
  scale_fill_manual(breaks=c("sum_sq_diff_emp","sum_sq_diff_lit"),
                       labels=c("Empirical", "Literature"),
                      name="Predicting",
                      values = c("purple", "orange"))+
  scale_alpha_manual(breaks=c("survey", "task"),
                     values = c(0.4, 0.7),
                     name="Measure type")+
  scale_color_discrete(name="Measure type")
```
